### 2022-06-28 paper/Chapters/Chapter02.tex
update dataset synthetic256

Guided method \cite{guided} requires addition information like RGB image for the inference.

%% denoising
The depth map captured by depth sensors are usually with full of missing pixels and holes.
\cite{depth-inpainting-distribution} proposed a depth hole filling method using the depth distributions of neighboring regions.

@@

%% method for structured point cloud

%% CNN based methods

estimate the surface normal based on improve the performance of image processing to a brand new stage. 
In 2014, Eigen et al.\cite{Eigen} proposed a method predicting depth map directly from RGB image using CNN. In this case, no depth map is required. In 2016, Laina et al. \cite{img2depth} proposed a deeper network based on ResNet \cite{resnet} with a well designed upsamling part. 
%% guided scene completion

\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image.

\cite{GeoNet} uses ResNet proposed by \cite{resnet} to infer the surface normal from RGB image, and further refine it with the help of depth map based on the methods proposed by \cite{geometry_based_solution}  further refine the a  GeoNet to infer depth and surface normal in one unified system,  method proposed by \cite{img2depth}.

@@

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\section{Normal Inference}

%% normal estimation method introduction
Usually, we based on point cloud, depth map or RGB/Grayscale image of the objects or scenes to inference the normals.

Traditional methods evaluate normals based on neighbor information of point cloud or depth map.
In 2012, Holzer et al. \cite{Holzer.S} proposed method to calculate normal from covariance matrices. 
This method use integral image as input, which is able to run algorithm in a high frame speed. They smooth the depth data in order to handle the noise of depth image. The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely. In 2013, Fouhey et al. \cite{geometry_based_solution} proposed a method constructing a over-determined function systems to predict normals and solving it 
by algebra methods. Similarly, this approach gives a quick but coarse normal inference.

>>>>

\section{Noise Handling}
%% denoising
The depth map captured by depth sensors are usually with full of missing pixels and holes.
\cite{depth-inpainting-distribution} proposed a depth hole filling method using the depth distributions of neighboring regions.

@@

%% normal estimation method introduction
\section{Surface normal inference}
\textbf{RGB based}  
\cite{Eigen} predicted depth map directly from RGB image. 
\cite{geometry_based_solution} proposed a method to learn discriminative and geometrically informative primitives from RGBD images, which is further used to recover the surface normals of a scene from a single image. 
\cite{GeoNet} uses ResNet (\cite{resnet}) to infer a coarse surface normal based on RGB image, and further refine it with the help of depth map based on the methods based on \cite{geometry_based_solution}.

\textbf{Point Cloud Based} 
\cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix. They also smooth the depth data in order to handle the noise of depth image. The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely.

\textbf{RGB-D based}
Guided method \cite{guided} requires addition information like RGB image for the inference.

%% method for structured point cloud
%% image based

@@
